Integrated approach to modeling to krill population dynamics in Wester Antarctic Peninsula: spatial and ecosystem considerations

### 2025-03-07 index.Rmd
test run

```{r message=FALSE, warning=FALSE, echo=TRUE}
dir01 <- here("s01") # agreggate data (no spatial diferences)
dir1<-here("s1") # Data strata flishery
dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
dir3<-here("s3") # whitout S-R
dir4<-here("s4") # 
dir5<-here("s5") # 
dir6<-here("s6") # 
dir7<-here("s7") # 2 set parametres EMM-2024/23 (Mardones)
dir8<-here("s8") # s1 test data weigthing
dir9<-here("s9") # s1 w/ blocks
dirtest<-here("test")
Figs <- here("Figs")# S
```

@@

#s9
base.model9 <- SS_output(dir=dir9,
                        covar=T,
                        forecast=T)

#stest
base.modeltest <- SS_output(dir=dirtest,
                        covar=T,
                        forecast=T)
```

@@

```{r}
SSplotTimeseries(base.modeltest,
                 subplot = 1)
SSplotTimeseries(base.modeltest,
                 subplot = 9)
```
and fits

@@

```{r }
SSplotData(base.model01, subplot = 1, 
           fleetnames = c("Fishery", "Survey", "Predator"),
           fleetcol = c("blue","green", "red"))

@@

# Crea el heatmap
ggplot(df1, aes(x = Yr, y = Bin, fill = Pearson)) +
  geom_tile() +
  scale_fill_gradient2(low = "blue", 
                       mid = "white", 
                       high = "red",
                       midpoint = 0) +
  facet_wrap(Fleet~., ncol=5) + 
  labs(title = "",
       x = "",
       y = "Length",
       fill = "Pearson") +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1))

@@

```{r eval=FALSE, message=FALSE, warning=FALSE}
#stest
retroModelstest <- SSgetoutput(dirvec=file.path(dirtest,
                                            "Retrospective",
                                            paste("retro",0:-3,
                                                  sep="")))

@@

```{r eval=FALSE}
retrotest <- SSplotRetro(retroSummarytest,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
```

@@

```{r}
hci = SSplotHCxval(retroSummary1, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

@@

```{r}
mvln = SSdeltaMVLN(base.model1,
                   Fref = "Btgt", 
                   plot = TRUE,
                   addprj=TRUE,
                   virgin = TRUE,
                   mc=100)

@@

```{r}
outps1 <- base.model1$timeseries[1:53, 2:8]

@@

# Crear los gráficos en un ciclo for
for (i in 1:length(data_list)) {
  p <- ggplot(data_list[[i]], aes(x = Yr, y = dev)) +
    geom_point() +
    stat_smooth(method = "loess", 
                span = 0.15, 
                se = T) +
    geom_hline(yintercept = 0,
               col="red",
               linetype = "dotdash")+
    ggtitle(titles[i]) +
    theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1))+
    theme_few()
  plots[[i]] <- p
}

>>>>

```{r message=FALSE, warning=FALSE, echo=TRUE}
dir01 <- here("s01") # agreggate data (no spatial diferences)
dir1<-here("s1") # Data strata flishery
dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
dir3<-here("s3") # without S-R
dir4<-here("s4") # 
dir5<-here("s5") # 
dir6<-here("s6") # 
dir7<-here("s7") # 2 set parametres EMM-2024/23 (Mardones)
dir8<-here("s8") # s1 platoons
dir9<-here("s9") # s1 w/ blocks
dirtest<-here("test")
Figs <- here("Figs")# S
```

@@

#s9
base.model9 <- SS_output(dir=dir9,
                        covar=T,
                        forecast=T)
```

```{r message=F, include=FALSE}
#stest
base.modeltest <- SS_output(dir=dirtest,
                        covar=T,
                        forecast=T)
```

@@

```{r}
SSplotTimeseries(base.modeltest,
                 subplot = 7)
SSplotTimeseries(base.modeltest,
                 subplot = 9)
```
and fits

@@

```{r }
SSplotData(base.modeltest, subplot = 1)

@@

# Crea el heatmap
ggplot(df1, aes(x = Yr, y = Bin, fill = Pearson)) +
  geom_tile() +
  scale_fill_gradient2(low = "blue", 
                       mid = "white", 
                       high = "red",
                       midpoint = 0) +
  facet_wrap(Fleet~., ncol=5) + 
  labs(title = "",
       x = "",
       y = "Length (cm)",
       fill = "Pearson") +
  theme_few()+
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1, 
                                   size = 7))

@@

```{r eval=FALSE, message=FALSE, warning=FALSE}
#stest
retroModelstest <- SSgetoutput(dirvec=file.path(dirtest,
                                            "Retrospective",
                                            paste("retro",0:-4,
                                                  sep="")))

@@

```{r eval=FALSE}
SSplotRetro(retroSummarytest,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
```

@@

```{r}
hci = SSplotHCxval(retroSummarytest, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

@@

```{r}
mvln = SSdeltaMVLN(base.modeltest,
                   Fref = "Btgt", 
                   plot = TRUE,
                   addprj=TRUE,
                   virgin = TRUE,
                   mc=100)

@@

```{r}
outps1 <- base.modeltest$timeseries[1:53, 2:8]

@@

for (i in 1:length(data_list)) {
  p <- ggplot(data_list[[i]], aes(x = Yr, y = dev)) +
    geom_point() +
    stat_smooth(method = "loess", 
                span = 0.15, 
                se = T) +
    geom_hline(yintercept = 0,
               col="red",
               linetype = "dotdash")+
    ggtitle(titles[i]) +
    theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1))+
    theme_few()
  plots[[i]] <- p
}
